---
title: 'LBB3 - UK Road Safety: Traffic Accidents (2005-2017)'
author: "Nadya"
date: "10/09/2020"
output: 
  html_document:
    toc: true
    toc_depth: 1
    toc_float: true
    code_folding: "hide"
    df_print: paged
    theme: "paper"
    highlight: "pygments"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# **Explanation** {.tabset}
## Brief 

Welcome!

For this LBB, this research will use UK Road Safety: Traffic Accidents (2005-2017).

reference: https://www.kaggle.com/tsiaras/uk-road-safety-accidents-and-vehicles

## Data's Point of View 

These files provide detailed road safety data about the circumstances of personal injury road accidents in GB from 1979, the types of vehicles involved and the consequential casualties. The statistics relate only to personal injury accidents on public roads that are reported to the police, and subsequently recorded, using the STATS19 accident reporting form.

<P>

# **Data Inspection** {.tabset}

## Library
```{r message=FALSE, error=FALSE, warning=FALSE}
library(lubridate)
library(dplyr)
library(ggpubr)
library(ggplot2)
library(scales)
library(RColorBrewer)
library(ggridges)
library(leaflet)
library(plotly)
library(viridis)
library(glue)
```


## Data source:
```{r data}
traffic<-read.csv("filtered_Accident_Information.csv")

```

## First 6 data
```{r data head}
head(traffic)
```


## last 6 data
```{r data tail}
tail(traffic)
```


## Data dimension
```{r data dim}
dim(traffic)
```


## Column Names
```{r data colnames}
names(traffic)
```


# **Data Cleansing & Coercion** {.tabset}

## check variable type
```{r data variable}
glimpse(traffic)
```

## Data Coertion {.tabset}

### Change to Factor/ Categorical
```{r data coertion to factor}
traffic$X1st_Road_Class <- as.factor(traffic$X1st_Road_Class)
traffic$X1st_Road_Number <- as.factor(traffic$X1st_Road_Number)
traffic$X2nd_Road_Class <- as.factor(traffic$X2nd_Road_Class)
traffic$X2nd_Road_Number <- as.factor(traffic$X2nd_Road_Number)
traffic$Accident_Severity <- as.factor(traffic$Accident_Severity)
traffic$Carriageway_Hazards <- as.factor(traffic$Carriageway_Hazards)
traffic$Day_of_Week <- as.factor(traffic$Day_of_Week)
traffic$Did_Police_Officer_Attend_Scene_of_Accident <- as.factor(traffic$Did_Police_Officer_Attend_Scene_of_Accident)
traffic$Junction_Control <- as.factor(traffic$Junction_Control)
traffic$Junction_Detail <- as.factor(traffic$Junction_Detail)
traffic$Light_Conditions <- as.factor(traffic$Light_Conditions)
traffic$Local_Authority_.District. <- as.factor(traffic$Local_Authority_.District.)
traffic$Local_Authority_.Highway. <- as.factor(traffic$Local_Authority_.Highway.)
traffic$Location_Easting_OSGR <- as.factor(traffic$Location_Easting_OSGR)
traffic$Location_Northing_OSGR <- as.factor(traffic$Location_Northing_OSGR)
traffic$LSOA_of_Accident_Location <- as.factor(traffic$LSOA_of_Accident_Location)
traffic$Police_Force <- as.factor(traffic$Police_Force)
traffic$Road_Surface_Conditions <- as.factor(traffic$Road_Surface_Conditions)
traffic$Road_Type <- as.factor(traffic$Road_Type)
traffic$Special_Conditions_at_Site <- as.factor(traffic$Special_Conditions_at_Site)
traffic$Speed_limit <- as.factor(traffic$Speed_limit)
traffic$Urban_or_Rural_Area <- as.factor(traffic$Urban_or_Rural_Area)
traffic$Weather_Conditions <- as.factor(traffic$Weather_Conditions)
traffic$InScotland <- as.factor(traffic$InScotland)
traffic$Year <- as.factor(traffic$Year)

```


### Change to Date
```{r message=FALSE, error=FALSE, warning=FALSE}

traffic$Date <- ymd(traffic$Date)

```

### Check variable type again
```{r data variable 2}
str(traffic)
```

```{r}
traffic
```


## Missing Value {.tabset}

### Showed any column that has `NULL` values
```{r}
colSums(is.na(traffic))
```


### Remove Column that Unrelated to This Research
```{r}
traffic <- subset(traffic, select = -c(X1st_Road_Class, 
                                       X1st_Road_Number, 
                                       X2nd_Road_Class, 
                                       X2nd_Road_Number, 
                                       Location_Easting_OSGR, 
                                       Location_Northing_OSGR))
```


### Remove Row that has NA value

```{r}
traffic <- na.omit(traffic, cols = c("Did_Police_Officer_Attend_Scene_of_Accident", 
                                     "Longitude", "Pedestrian_Crossing.Human_Control", 
                                     "Pedestrian_Crossing.Physical_Facilities", 
                                     "Speed_limit", 
                                     "InScotland"))
```


### Check The Table Again

```{r}
traffic
```




# **Data Explanation** {.tabset}

## Brief Explanation

```{r data summary}
glimpse(traffic)
```


# **Data Preparation** {.tabset}

## Brief Explanation

```{r data summary}
glimpse(traffic)
```


## Create Data Frame

<h3>Junction Control</h3>

```{r message=FALSE, error=FALSE, warning=FALSE}
plot_Junction_Control <- traffic %>% 
  group_by(Accident_Severity, Junction_Control) %>%
  dplyr::summarise(n_Junction_Control = n()) %>% 
  arrange(- n_Junction_Control) %>% 
  group_by(Accident_Severity) %>% 
  mutate(freq_Junction_Control = prop.table(n_Junction_Control))

join_Junction_COntrol <- left_join(traffic, plot_Junction_Control, by = c("Accident_Severity" = "Accident_Severity", "Junction_Control" = "Junction_Control"))
```


<h3>Junction Detail </h3>

```{r message=FALSE, error=FALSE, warning=FALSE}
plot_Junction_Detail <- traffic %>% 
  group_by(Accident_Severity, Junction_Detail) %>%
  dplyr::summarise(n_Junction_Detail = n()) %>% 
  arrange(- n_Junction_Detail) %>% 
  group_by(Accident_Severity) %>% 
  mutate(freq_Junction_Detail = prop.table(n_Junction_Detail))

join_Junction_Detail <- left_join(traffic, plot_Junction_Detail, by = c("Accident_Severity" = "Accident_Severity", "Junction_Detail" = "Junction_Detail"))
```


<h3>Urban/Rural Area</h3>

```{r message=FALSE, error=FALSE, warning=FALSE}
plot_Urban_or_Rural_Area <- traffic %>% 
  group_by(Accident_Severity, Urban_or_Rural_Area) %>%
  dplyr::summarise(n_Urban_or_Rural_Area = n()) %>% 
  arrange(- n_Urban_or_Rural_Area) %>% 
  group_by(Accident_Severity) %>% 
  mutate(freq_Urban_or_Rural_Area = prop.table(n_Urban_or_Rural_Area))

join_Urban_or_Rural_Area <- left_join(traffic, plot_Urban_or_Rural_Area, by = c("Accident_Severity" = "Accident_Severity", "Urban_or_Rural_Area" = "Urban_or_Rural_Area"))
```


<h3>Road Type</h3>

```{r message=FALSE, error=FALSE, warning=FALSE}
plot_Road_Type <- traffic %>% 
  group_by(Accident_Severity, Road_Type) %>%
  dplyr::summarise(n_Road_Type = n()) %>% 
  arrange(- n_Road_Type) %>% 
  group_by(Accident_Severity) %>% 
  mutate(freq_Road_Type = prop.table(n_Road_Type))

join_Road_Type <- left_join(traffic, plot_Road_Type, by = c("Accident_Severity" = "Accident_Severity", "Road_Type" = "Road_Type"))
```


<h3>Road Survey COndition</h3>

```{r message=FALSE, error=FALSE, warning=FALSE}
plot_Road_Surface_Conditions <- traffic %>% 
  group_by(Accident_Severity, Road_Surface_Conditions) %>%
  dplyr::summarise(n_Road_Surface_Conditions = n()) %>% 
  arrange(- n_Road_Surface_Conditions) %>% 
  group_by(Accident_Severity) %>% 
  mutate(freq_Road_Surface_Conditions = prop.table(n_Road_Surface_Conditions))

join_Road_Surface_Conditions <- left_join(traffic, plot_Road_Surface_Conditions, by = c("Accident_Severity" = "Accident_Severity", "Road_Surface_Conditions" = "Road_Surface_Conditions"))
```


<h3>Speed Limit</h3>

```{r message=FALSE, error=FALSE, warning=FALSE}
plot_Speed_limit <- traffic %>% 
  group_by(Accident_Severity, Speed_limit) %>%
  dplyr::summarise(n_Speed_limit = n()) %>% 
  arrange(- n_Speed_limit) %>% 
  group_by(Accident_Severity) %>% 
  mutate(freq_Speed_limit = prop.table(n_Speed_limit))

join_Speed_limit <- left_join(traffic, plot_Speed_limit, by = c("Accident_Severity" = "Accident_Severity", "Speed_limit" = "Speed_limit"))
```


<h3>Weather Condition</h3>

```{r message=FALSE, error=FALSE, warning=FALSE}
plot_Weather_Conditions <- traffic %>% 
  group_by(Accident_Severity, Weather_Conditions) %>%
  dplyr::summarise(n_Weather_Conditions = n()) %>% 
  arrange(- n_Weather_Conditions) %>% 
  group_by(Accident_Severity) %>% 
  mutate(freq_Weather_Conditions = prop.table(n_Weather_Conditions))

join_Weather_Conditions <- left_join(traffic, plot_Weather_Conditions, by = c("Accident_Severity" = "Accident_Severity", "Weather_Conditions" = "Weather_Conditions"))
```



<h3>Light Condition</h3>

```{r message=FALSE, error=FALSE, warning=FALSE}
plot_Light_Conditions <- traffic %>% 
  group_by(Accident_Severity, Light_Conditions) %>%
  dplyr::summarise(n_Light_Conditions = n()) %>% 
  arrange(- n_Light_Conditions) %>% 
  group_by(Accident_Severity) %>% 
  mutate(freq_Light_Conditions = prop.table(n_Light_Conditions))

join_Light_Conditions <- left_join(traffic, plot_Light_Conditions, by = c("Accident_Severity" = "Accident_Severity", "Light_Conditions" = "Light_Conditions"))
```


```{r}
traffic_new <- traffic %>% 
  select(Accident_Severity, Junction_Control, Junction_Detail, Urban_or_Rural_Area, Road_Type, Road_Surface_Conditions, Speed_limit, Weather_Conditions, Light_Conditions)

traffic_new <- left_join(traffic_new, plot_Junction_Control, by = c("Accident_Severity" = "Accident_Severity", "Junction_Control" = "Junction_Control"))
traffic_new <- left_join(traffic_new, plot_Junction_Detail, by = c("Accident_Severity" = "Accident_Severity", "Junction_Detail" = "Junction_Detail"))
traffic_new <- left_join(traffic_new, plot_Urban_or_Rural_Area, by = c("Accident_Severity" = "Accident_Severity", "Urban_or_Rural_Area" = "Urban_or_Rural_Area"))
traffic_new <- left_join(traffic_new, plot_Road_Type, by = c("Accident_Severity" = "Accident_Severity", "Road_Type" = "Road_Type"))
traffic_new <- left_join(traffic_new, plot_Road_Surface_Conditions, by = c("Accident_Severity" = "Accident_Severity", "Road_Surface_Conditions" = "Road_Surface_Conditions"))
traffic_new <- left_join(traffic_new, plot_Speed_limit, by = c("Accident_Severity" = "Accident_Severity", "Speed_limit" = "Speed_limit"))
traffic_new <- left_join(traffic_new, plot_Weather_Conditions, by = c("Accident_Severity" = "Accident_Severity", "Weather_Conditions" = "Weather_Conditions"))
traffic_new <- left_join(traffic_new, plot_Light_Conditions, by = c("Accident_Severity" = "Accident_Severity", "Light_Conditions" = "Light_Conditions"))
```


```{r}
ok <- traffic %>% 
  select(Accident_Severity,Year, Junction_Control, Junction_Detail, Urban_or_Rural_Area, Road_Type, Road_Surface_Conditions, Speed_limit, Weather_Conditions, Light_Conditions)

ok <- left_join(ok, plot_Junction_Control, by = c("Accident_Severity" = "Accident_Severity", "Junction_Control" = "Junction_Control")) %>% 
  left_join(., plot_Junction_Detail, by = c("Accident_Severity" = "Accident_Severity", "Junction_Detail" = "Junction_Detail")) %>% 
  left_join(., plot_Urban_or_Rural_Area, by = c("Accident_Severity" = "Accident_Severity", "Urban_or_Rural_Area" = "Urban_or_Rural_Area")) %>% 
  left_join(., plot_Road_Type, by = c("Accident_Severity" = "Accident_Severity", "Road_Type" = "Road_Type")) %>% 
  left_join(., plot_Road_Surface_Conditions, by = c("Accident_Severity" = "Accident_Severity", "Road_Surface_Conditions" = "Road_Surface_Conditions")) %>% 
  left_join(., plot_Speed_limit, by = c("Accident_Severity" = "Accident_Severity", "Speed_limit" = "Speed_limit")) %>% 
  left_join(., plot_Weather_Conditions, by = c("Accident_Severity" = "Accident_Severity", "Weather_Conditions" = "Weather_Conditions")) %>% 
  left_join(., plot_Light_Conditions, by = c("Accident_Severity" = "Accident_Severity", "Light_Conditions" = "Light_Conditions")) %>% 
  distinct()

```


```{r}
traffic_factor <- traffic %>% 
  select(Accident_Severity, Police_Force, Local_Authority_.District., Junction_Control, Junction_Detail, Urban_or_Rural_Area, Road_Type, Road_Surface_Conditions, Speed_limit, Weather_Conditions, Light_Conditions, Longitude, Latitude)

traffic_factor <- left_join(traffic_factor, plot_Junction_Control, by = c("Accident_Severity" = "Accident_Severity", "Junction_Control" = "Junction_Control")) %>% 
  left_join(., plot_Junction_Detail, by = c("Accident_Severity" = "Accident_Severity", "Junction_Detail" = "Junction_Detail")) %>% 
  left_join(., plot_Urban_or_Rural_Area, by = c("Accident_Severity" = "Accident_Severity", "Urban_or_Rural_Area" = "Urban_or_Rural_Area")) %>% 
  left_join(., plot_Road_Type, by = c("Accident_Severity" = "Accident_Severity", "Road_Type" = "Road_Type")) %>% 
  left_join(., plot_Road_Surface_Conditions, by = c("Accident_Severity" = "Accident_Severity", "Road_Surface_Conditions" = "Road_Surface_Conditions")) %>% 
  left_join(., plot_Speed_limit, by = c("Accident_Severity" = "Accident_Severity", "Speed_limit" = "Speed_limit")) %>% 
  left_join(., plot_Weather_Conditions, by = c("Accident_Severity" = "Accident_Severity", "Weather_Conditions" = "Weather_Conditions")) %>% 
  left_join(., plot_Light_Conditions, by = c("Accident_Severity" = "Accident_Severity", "Light_Conditions" = "Light_Conditions")) %>% 
  distinct()
```



```{r}
traffic_factor %>% 
  filter(Police_Force == "City of London")
```



## Data Insight {.tabset}

### WHICH PERIOD MOSTLY ACCIDENT HAPPENS?

```{r}
plot_Year <- traffic %>%
  group_by(Accident_Severity, Year) %>% 
  dplyr::summarise(n_Year = n()) %>% 
  mutate(freq_Year = prop.table(n_Year))

```


```{r}
plot_Day <- traffic %>%
  group_by(Accident_Severity, Day_of_Week) %>% 
  dplyr::summarise(n_Day = n()) %>% 
  arrange(- n_Day)
```

```{r}
traffic_DateTime <- traffic %>% 
  select(Accident_Severity, Year, Day_of_Week, Police_Force, Local_Authority_.District., Junction_Control, Junction_Detail, Urban_or_Rural_Area, Road_Type, Road_Surface_Conditions, Speed_limit, Weather_Conditions, Light_Conditions)

traffic_DateTime <- left_join(traffic_DateTime, plot_Year, by = c("Accident_Severity" = "Accident_Severity", "Year" = "Year")) %>% 
  left_join(., plot_Day, by = c("Accident_Severity" = "Accident_Severity", "Day_of_Week" = "Day_of_Week"))
```


#### Year

```{r message=FALSE, error=FALSE, warning=FALSE}
traffic %>%
  group_by(Accident_Severity, Year) %>% 
  dplyr::summarise(n_Year = n()) %>% 
  mutate(freq_Year = prop.table(n_Year)) %>% 
  ggplot(aes(x = Year,
             y = n_Year,
             fill = Accident_Severity)) +
  geom_col(stat = "identity") +
  theme_bw() +
  scale_fill_manual(values = rev(brewer.pal(15, "Set3"))) +
  labs(title = "Traffic per Year X Accident Severity",
       subtitle = "(2005-17)",
       x = "Year",
       y = "Freq")
```

#### Day of Week

```{r}

traffic %>%
  group_by(Accident_Severity, Day_of_Week) %>% 
  dplyr::summarise(n_Day = n()) %>% 
  arrange(- n_Day) %>% 
  ggplot(aes(reorder(x = Day_of_Week, -n_Day),
             y = n_Day,
             fill = Accident_Severity)) +
  geom_col(position = "stack", stat = "identity") +
  theme_bw() +
  scale_fill_manual(values = rev(brewer.pal(7, "Set3"))) +
  labs(title = "Traffic per Day X Accident Severity",
       subtitle = "(2005-17)",
       x = "Day of Week",
       y = "Freq")
```



### WHICH VARIABLE HAS THE MOST IMPACT? {.tabset}

#### Junction Control

```{r message=FALSE, error=FALSE, warning=FALSE}
fig_Junction_Control <- plot_Junction_Control %>%
  group_by(Accident_Severity, Junction_Control) %>% 
  mutate(mytext = paste(
    "Junction Control: ", Junction_Control , "\n",
    "Count: ", number(n_Junction_Control, big.mark = ',', accuracy = 1),
    sep="")) %>%  
  ggplot(aes(fill=Junction_Control, 
             y=n_Junction_Control, 
             x=Accident_Severity,)) + 
  geom_bar(aes(text = mytext),
           position="fill", 
           stat="identity") +
  theme_bw() +
  labs(title = "Accident Severity X Junction Control",
       subtitle = "(2005-17)",
       x = "Accident Severity",
       y = "Percentage") +
  scale_fill_manual(values = rev(brewer.pal(7, "Set3")))

fig_Junction_Control <- ggplotly(fig_Junction_Control, tooltip="text")
fig_Junction_Control

```


#### Junction Detail

```{r message=FALSE, error=FALSE, warning=FALSE}
fig_Junction_Detail <- plot_Junction_Detail %>%
  group_by(Accident_Severity, Junction_Detail) %>% 
  mutate(mytext = paste(
    "Junction Detail: ", Junction_Detail , "\n",
    "Count: ", number(n_Junction_Detail, big.mark = ',', accuracy = 1),
    sep="")) %>%  
  ggplot(aes(fill=Junction_Detail, 
             y=n_Junction_Detail, 
             x=Accident_Severity,)) + 
  geom_bar(aes(text = mytext),
           position="fill", 
           stat="identity") +
  theme_bw() +
  labs(title = "Accident Severity X Junction Detail",
       subtitle = "(2005-17)",
       x = "Accident Severity",
       y = "Percentage") +
  scale_fill_manual(values = rev(brewer.pal(11, "Set3")))

fig_Junction_Detail <- ggplotly(fig_Junction_Detail, tooltip="text")
fig_Junction_Detail

```


#### Urban/Rural Area

```{r message=FALSE, error=FALSE, warning=FALSE}
fig_Urban_or_Rural_Area <- plot_Urban_or_Rural_Area %>%
  group_by(Accident_Severity, Urban_or_Rural_Area) %>% 
  mutate(mytext = paste(
    "Area: ", Urban_or_Rural_Area , "\n",
    "Count: ", number(n_Urban_or_Rural_Area, big.mark = ',', accuracy = 1),
    sep="")) %>%  
  ggplot(aes(fill=Urban_or_Rural_Area, 
             y=n_Urban_or_Rural_Area, 
             x=Accident_Severity,)) + 
  geom_bar(aes(text = mytext),
           position="fill", 
           stat="identity") +
  theme_bw() +
  labs(title = "Accident Severity X Urban/Rural Area",
       subtitle = "(2005-17)",
       x = "Accident Severity",
       y = "Percentage") +
  scale_fill_manual(values = rev(brewer.pal(4, "Set3")))

fig_Urban_or_Rural_Area <- ggplotly(fig_Urban_or_Rural_Area, tooltip="text")
fig_Urban_or_Rural_Area

```


#### Road Type

```{r message=FALSE, error=FALSE, warning=FALSE}
fig_Road_Type <- plot_Road_Type %>%
  group_by(Accident_Severity, Road_Type) %>% 
  mutate(mytext = paste(
    "Road Type: ", Road_Type , "\n",
    "Count: ", number(n_Road_Type, big.mark = ',', accuracy = 1),
    sep="")) %>%  
  ggplot(aes(fill=Road_Type, 
             y=n_Road_Type, 
             x=Accident_Severity,)) + 
  geom_bar(aes(text = mytext),
           position="fill", 
           stat="identity") +
  theme_bw() +
  labs(title = "Accident Severity X Road Type",
       subtitle = "(2005-17)",
       x = "Accident Severity",
       y = "Percentage") +
  scale_fill_manual(values = rev(brewer.pal(15, "Set3")))

fig_Road_Type <- ggplotly(fig_Road_Type, tooltip="text")
fig_Road_Type

```


#### Road Survey Condition

```{r message=FALSE, error=FALSE, warning=FALSE}
fig_Road_Surface_Conditions <- plot_Road_Surface_Conditions %>%
  group_by(Accident_Severity, Road_Surface_Conditions) %>% 
  mutate(mytext = paste(
    "Road Survey Condition: ", Road_Surface_Conditions , "\n",
    "Count: ", number(n_Road_Surface_Conditions, big.mark = ',', accuracy = 1),
    sep="")) %>%  
  ggplot(aes(fill=Road_Surface_Conditions, 
             y=n_Road_Surface_Conditions, 
             x=Accident_Severity,)) + 
  geom_bar(aes(text = mytext),
           position="fill", 
           stat="identity") +
  theme_bw() +
  labs(title = "Accident Severity X Road Survey Condition",
       subtitle = "(2005-17)",
       x = "Accident Severity",
       y = "Percentage") +
  scale_fill_manual(values = rev(brewer.pal(8, "Set3")))

fig_Road_Surface_Conditions <- ggplotly(fig_Road_Surface_Conditions, tooltip="text")
fig_Road_Surface_Conditions
```


#### Speed Limit

```{r message=FALSE, error=FALSE, warning=FALSE}
fig_Speed_limit <- plot_Speed_limit %>%
  group_by(Accident_Severity, Speed_limit) %>% 
  mutate(mytext = paste(
    "Speed Limit: ", Speed_limit , "\n",
    "Count: ", number(n_Speed_limit, big.mark = ',', accuracy = 1),
    sep="")) %>%  
  ggplot(aes(fill=Speed_limit, 
             y=n_Speed_limit, 
             x=Accident_Severity,)) + 
  geom_bar(aes(text = mytext),
           position="fill", 
           stat="identity") +
  theme_bw() +
  labs(title = "Accident Severity X Speed Limit",
       subtitle = "(2005-17)",
       x = "Accident Severity",
       y = "Percentage") +
  scale_fill_manual(values = rev(brewer.pal(15, "Set3")))

fig_Speed_limit <- ggplotly(fig_Speed_limit, tooltip="text")
fig_Speed_limit

```


#### Weather Condition

```{r message=FALSE, error=FALSE, warning=FALSE}
fig_Weather_Conditions <- plot_Weather_Conditions %>%
  group_by(Accident_Severity, Weather_Conditions) %>% 
  mutate(mytext = paste(
    "Weather Condition: ", Weather_Conditions , "\n",
    "Count: ", number(n_Weather_Conditions, big.mark = ',', accuracy = 1),
    sep="")) %>%  
  ggplot(aes(fill=Weather_Conditions, 
             y=n_Weather_Conditions, 
             x=Accident_Severity,)) + 
  geom_bar(aes(text = mytext),
           position="fill", 
           stat="identity") +
  theme_bw() +
  labs(title = "Accident Severity X Weather Condition",
       subtitle = "(2005-17)",
       x = "Accident Severity",
       y = "Percentage") +
  scale_fill_manual(values = rev(brewer.pal(15, "Set3")))

fig_Weather_Conditions <- ggplotly(fig_Weather_Conditions, tooltip="text")
fig_Weather_Conditions

```



#### Light Condition


```{r}
fig_Light_Conditions <- plot_Light_Conditions %>%
  group_by(Accident_Severity, Light_Conditions) %>% 
  mutate(mytext = paste(
    "Light Condition: ", Light_Conditions , "\n",
    "Count: ", number(n_Light_Conditions, big.mark = ',', accuracy = 1),
    sep="")) %>%  
  ggplot(aes(fill=Light_Conditions, 
             y=n_Light_Conditions, 
             x=Accident_Severity,)) + 
  geom_bar(aes(text = mytext),
           position="fill", 
           stat="identity") +
  theme_bw() +
  labs(title = "Accident Severity X Light Condition",
       subtitle = "(2005-17)",
       x = "Accident Severity",
       y = "Percentage") +
  scale_fill_manual(values = rev(brewer.pal(9, "Set3")))

fig_Light_Conditions <- ggplotly(fig_Light_Conditions, tooltip="text")
fig_Light_Conditions
```


**Area**
```{r}
area <- traffic %>%
  # select(Accident_Index, Accident_Severity, Police_Force, Local_Authority_.District., Longitude, Latitude, Number_of_Casualties) %>%  
  filter(Accident_Severity == "Fatal") %>%
  group_by(Police_Force) %>% 
  mutate(Accident_Severity = factor(Accident_Severity, unique(Accident_Severity)),
         Police_Force = factor(Police_Force, unique(Police_Force)),
         Local_Authority_.District. = factor(Local_Authority_.District., unique(Local_Authority_.District.)),
         ) %>%
  ungroup() %>% 
  group_by(Local_Authority_.District.) %>% 
  mutate(
    mytext = paste(
    "Accident Index: ", Accident_Index, "\n",
    "Jurisdiction: ", Police_Force , " / " , Local_Authority_.District., "\n",
    "Date: ", Day_of_Week, ", ", Date, " ", Time  , "\n",    
    "Report: ", Number_of_Casualties, " casualties from ", Number_of_Vehicles, " vehicles" ,"\n",
    "Junction: ", Junction_Control, " / ", Junction_Detail ,"\n",
    "Road : ", Road_Type, " / ", Road_Surface_Conditions, " / ", Weather_Conditions, " / ", Light_Conditions ,"\n",
    "Speed Limit: ", Speed_limit, "\n",
    sep="")) %>%
  ggplot(aes(x = Longitude, y = Latitude)) +
  geom_point(aes(x = Longitude,
                 y = Latitude,
                 text = mytext,
                 fill= Police_Force,
                 group = Local_Authority_.District.,)) +
  scale_size_continuous(range=c(1,15)) +
  theme_void() + 
  ylim(50,59) + 
  coord_map() +
  theme(legend.position="none")
  
area <- ggplotly(area, tooltip="text")
area
  
```


**Cluster**
```{r}
traffic %>% 
  filter(Accident_Severity == "Fatal") %>% 
  group_by(Local_Authority_.District.) %>%
  leaflet() %>% 
  setView( lng = -1.9, lat = 55, zoom = 5 ) %>% 
  addProviderTiles("Esri") %>%
  addMarkers(lng = ~Longitude,
             lat = ~Latitude,
             clusterOptions = markerClusterOptions())
```



```{r}
list(colnames(traffic_DateTime))
```

